Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
refactor start of section IV

\section{Feature design}
\label{sec:design}
\ja{It seems that what we are doing in this section is more post-processing than feature design, which would be the scattering transform itself.}

Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power.
In this section, we review three ways of achieving these properties, namely logarithmic compression, and temporal integration, and standardization.

>>>>

\section{Feature design}
\label{sec:design}

Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power.
In this section, we review three ways of achieving these properties, namely logarithmic compression, and temporal integration, and standardization.
Whether we adopt a time-frequency perspective or a machine learning perspective on the problem of acoustic scene classification, such operations would either be qualifies as post-processing or pre-processing.
